\thesistitle

### 2019-07-25 sections/results.tex
Results

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=.5\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

@@

We also measured the duration of finding clones by the different clone types. Fig.~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types. The reason for this is further explained in Sec.~\ref{chap:challenge}.

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=.5\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

@@

\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
We analyzed the context of clones in a large corpus of open source projects. For these experiments, we used our CloneRefactor tool. These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  the content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.

\subsection{Clone detection results}
Currently, we have implemented two clone detection algorithms into CloneRefactor. The first one finds clones by comparing tokens (excluding whitespace, comments and newlines), equal to the definition of type 1 clones in literature \cite{roy2007survey}. The second algorithm implements our type 1R, as explained in chapter \ref{chap:type1clones}. The differences between the clones found for these algorithms is displayed in Table \ref{table:clonedet}.

\begin{table}[H]
  \begin{center}
  \caption{CloneRefactor clone detection results for the two different algorithms.} \label{table:clonedet}
  \medskip
\begin{tabular}{|l|l|l|}
\hline
 & \textbf{Type 1} & \textbf{Type 1R} \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of lines cloned\end{tabular} & 200,362 & 129,519 \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of statements/\\declarations cloned\end{tabular} & 182,466 & 118,980 \\ \hline
\begin{tabular}[c]{@{}l@{}}Amount of tokens cloned\end{tabular} & 1,582,845 & 973,596 \\ \hline
\end{tabular}
\end{center}
\end{table}

Looking at Table \ref{table:clonedet}, it becomes apparent that the type 1R algorithm finds significantly less clones than the type 1 algorithm. This indicates that about a third of the clones have textual equality, but are not actually equal when considering the types of expressions. This makes these clones less suitable for automated refactoring.

\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
In section \ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.

@@

\subsection{Clone instance location}\label{chap:clonelocation}
Measuring the clone locations categories defined in section \ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.

@@

\section{Clone instance contents}\label{chap:clonecontents}
Measuring the clone contents categories defined in section \ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.

@@

\section{Merging duplicate code through refactoring} \label{sec:refactorability}
In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction. Our results are displayed in Table \ref{table:refactorability}.

>>>>

\begin{figure}[H]
  \centering
    \includegraphics[width=.5\columnwidth]{img/TypeResults}
      \caption{Number of cloned declarations/statements.}
  \label{fig:typeres}
\end{figure}

@@

We also measured the duration of finding clones by the different clone types. Figure~\ref{fig:performance} shows the duration of detecting all clones in the corpus using CloneRefactor for different clone types. Although this data is partly dependent on our implementation of the clone types, there is a notable difference between the refactoring-oriented clone types and the literature clone types. The reason for this is further explained in section~\ref{chap:challenge}.

\begin{figure}[H]
  \centering
    \includegraphics[width=.5\columnwidth]{img/DurationChart}
    \caption{Duration in minutes of identifying clones for clone type definitions.}
  \label{fig:performance}
\end{figure}

@@

\section{Context Analysis of Clones}\label{chap:clonecontextexpl}
We analyzed the context of clones in a large corpus of open source projects. For these experiments, we used our CloneRefactor tool. These experiments follow the structure of the context: The relation between clone instances is explained, measured and discussed in chapter \ref{chap:relationsinstances}; the location of clone instances is explained, measured and discussed in chapter \ref{chap:clonelocation};  he content of clone instances are explained, measured and discussed in chapter \ref{chap:clonecontents}.

\subsection{Relations Between Clone Instances} \label{chap:relationsinstances}
\todo{update these results}
In section \ref{sec:setuprelation} we introduced our experiments regarding relations between clones. Table~\ref{table:relations} contains our results regarding the relations between clone instances.

@@

\subsection{Clone instance location}\label{chap:clonelocation}
\todo{update these results}
Measuring the clone locations categories defined in section \ref{sec:setuplocation} yields the results displayed in Table \ref{table:contents}.

@@

\section{Clone instance contents}\label{chap:clonecontents}
\todo{update these results}
Measuring the clone contents categories defined in section \ref{sec:setupcontents} yields the results displayed in Table \ref{table:contents}.

@@

\section{Merging duplicate code through refactoring} \label{sec:refactorability}
\todo{update these results}
In section \ref{sec:refactorabilitysetup} we define catagories regarding the extent to which clones can be refactored through method extraction. Our results are displayed in Table \ref{table:refactorability}.
